---
title: "analysis"
date: "8/23/2019"
output: html_document
---

## Setup

```{r setup}
library(tidyverse)
library(ggridges)
library(pwr) 
library(grid)
library(gtable)

library(boot)
library(bootES)


library(ggbeeswarm)

library(tidybayes)
library(cowplot)
library(broom)

theme_set(theme_tidybayes() + panel_border() + background_grid())


#df <- read.csv("../results/pilot/CSV/TidyR.csv")
df <- read.csv("../results/pilot/CSV/TidyR.csv")
dfp <- read.csv("../results/pilot/CSV/participantInfoTidyR.csv")
```


```{r fig.width=10, fig.height=4 }


filteredData <- dfp %>% 
  filter(type=="feedback")


  filteredData$value = as.numeric( as.character(filteredData$value ))
  
  print(filteredData)
  g<- filteredData %>% 
  ggplot( aes(x=measure, y=value) ) +
    geom_jitter( shape=1 , colour = "grey", position = position_jitter(w = 0.3, h = 0)) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.5) +
  # ylim(0,100) +
   # xlim(-.25,.25) +
  coord_flip() +
  labs(y="Score", x = 'Feedback Question')

    # facet_grid(. ~ userDriven)

# testData <- ggplot_build(g)$data
stg <- ggplot_build(g)$data[[2]]
print (stg)

# //add userDriven column

# stg$userDriven <- ifelse(stg$PANEL==1, "manual", "supported")
g + geom_text(data = stg,
              aes(x = x, y = 0.85, label = round(y,2)),
              color = "blue", size=3,
              vjust = 1)  +
  # facet_grid(. ~ userDriven)+
   labs(y="Score", x = 'Feedback Question')
```


## Data Cleaning / Types

```{r}

# labels.userDriven <- c(manual = 'Manual', supported = 'Supported');

df_acc <- df %>% 
  filter(measure=="accuracy") %>% 
mutate( userDriven = as.character(userDriven) ) 

df_acc$value = as.numeric( as.character(df_acc$value )) 

df_time <- df %>% 
  filter(measure=="secondsOnTask") 

df_time$value = as.numeric( as.character(df_time$value ))

```

## Quick Check Charts

95% CIs + jitter (don't trust those point positions)

```{r fig.width=5, fig.height=8 }

df_acc$custom_group <- ifelse(df_acc$taskDifficulty=='easy', "easy", "medium_hard")
df_time$custom_group <- ifelse(df_time$taskDifficulty=='easy', "easy", "medium_hard")



df_time %>% 
  ggplot( aes(x=userDriven, y=value) ) +
    geom_jitter( shape=1 , color="grey", position = position_jitter(w = 0.1, h = 0)) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.5) +
  ylim(0,100) +
   # xlim(-.25,.25) +
  coord_flip() +
    facet_grid(group ~ .)+
  theme(strip.text.y = element_text(angle=0))

# testData <- ggplot_build(g)$data
stg <- ggplot_build(g)$data[[2]]
print (stg)

# //add userDriven column

# stg$userDriven <- ifelse(stg$PANEL==1, "manual", "supported")
# g + geom_text(data = stg,
#               aes(x = x, y = 0.1, label = round(y,3)),
#               color = "blue", size=3,
#               vjust = 1)  +
#   facet_grid(. ~ userDriven)+
#    labs(y="Accuracy", x = 'Task Group')
```


```{r fig.width=8, fig.height=6 }

userDriven.colors <- c(manual ="#05b4dd", supported = "#f4aa4a")



df_acc$custom_group <- ifelse(df_acc$taskDifficulty=='easy', "easy", "medium_hard")
df_time$custom_group <- ifelse(df_time$taskDifficulty=='easy', "easy", "medium_hard")

df_medium_hard = df_acc %>%
  filter(custom_group=="medium_hard")

# df_medium_hard = df_time

g<-df_medium_hard %>% 
  ggplot( aes(x=userDriven, y=value, fill = userDriven, color = userDriven) ) +
    facet_grid(taskType ~ .)+

    # geom_jitter( shape=16 , colour='grey', alpha=0.7, size=2, position = position_jitter(w = 0.3, h = 0)) +
    geom_violin(show.legend=FALSE) +

    stat_summary(fun.data = "mean_cl_boot", geom="linerange", size=1,alpha=1, colour = "#5c5c5c", show.legend=FALSE) +
    stat_summary(fun.data = "mean_cl_boot", colour = "#5c5c5c", size = 1, alpha=0.5, show.legend=FALSE) +
 
  # ylim(0,100) +
   # ylim(0,100) +
  coord_flip() +
      scale_color_manual(values=userDriven.colors)+
  scale_fill_manual(values=userDriven.colors)




# 
# 
# testData <- ggplot_build(g)$data
stt <- ggplot_build(g)$data[[3]]
print (stt)

# //TIME
# stt$PANEL <- as.numeric( as.character(stt$PANEL ))
# stt$taskType <- ifelse((stt$PANEL <3), "cluster", ifelse((stt$PANEL <5), "linear regression", ifelse((stt$PANEL <7), "outlier", ifelse((stt$PANEL <9), "quadratic regression", "skyline"))))
#
# stt$custom_group <- ifelse(stt$PANEL%%2 == 0, "medium_hard", "easy")
# stt$userDriven <- ifelse(stt$group=="1", 'manual', 'supported')


# ACCURACY
stt$PANEL <- as.numeric( as.character(stt$PANEL ))
stt$taskType <- ifelse((stt$PANEL <2), "cluster", ifelse((stt$PANEL <3), "linear regression", ifelse((stt$PANEL <4), "outlier", ifelse((stt$PANEL <5), "quadratic regression", "skyline"))))

stt$custom_group <- ifelse(stt$PANEL%%2 == 0, "medium_hard", "medium_hard")
stt$userDriven <- ifelse(stt$group=="1", 'manual', 'supported')





print (stt)
g + geom_text(data = stt,
              aes(x =userDriven, y = 0.05, label = paste(round(y,3) , '[' , round(ymin,3) ,  ',' , round(ymax,3) , ']',sep=" ")),
             color = "black",size=3,
              vjust = 1)  +
   facet_grid(taskType ~ .)+
   labs(y="Accuracy", x = 'Mode')

filename <- paste("results_violin_scatter.pdf")
 ggsave(filename, width = 8, height = 6, units = "in")


 
 
```

```{r}

vplot <- function(task) {
  
  print(task)

sdf = df %>% filter( taskId == task )
tt = as.character(sdf[1,]$taskTitle)
prompt = as.character(sdf[1,]$taskPrompt)
number = as.character(sdf[1,]$taskNumber)

acc_stats = wilcox %>% filter( taskNumber == number & measure == "accuracy" )
time_stats = wilcox %>% filter( taskNumber == number & measure == "time" )

ci_acc_NL = ci_values %>% filter( taskNumber == number & measure == "accuracy" & vis== 'nodeLink' )
ci_acc_AM = ci_values %>% filter( taskNumber == number & measure == "accuracy"  & vis== 'adjMatrix' )

ci_time_NL = ci_values %>% filter( taskNumber == number & measure == "time" & vis== 'nodeLink' )
ci_time_AM = ci_values %>% filter( taskNumber == number & measure == "time"  & vis== 'adjMatrix' )


gridLines <- function(x) { 
  if (max(x) < 2) seq(0, 1, .25) 
  else if (max(x) == 7.3) seq (1,7,2)
    else seq(0,6,2) 
}

axisRange <- function(x) { 
  if (max(x) < 2) c(0, 1) 
  else if (max(x) == 7) c(1,7)
    else c(0,6) 
}

gridLabels <- function(x) { 
  if (max(as.numeric(x)) < 1.1) seq(0, 1, .5) 
  else if (max(as.numeric(x)) == 7.3) seq (1,7,2)
    else seq(0, 5,1 )
    #else seq(0, round(max(x)), round(max(x)/3)) 
}

ymin <- function(values, args) {
  # yValues <- ci_values %>% 
  # filter(taskId == task & measure==measure_) 
  # 
  # print(strsplit(yValues$M, 'M='))
# df_tmp$value = as.numeric( as.character(df_tmp$value ))
# 
# nl = df_tmp %>% 
#   filter(taskId == task & visType == "nodeLink")
# 
# adj = df_tmp %>% 
#   filter(taskId == task & visType == "adjMatrix")
# 
  
  
  print(args)
  return(0.75)
}


ciboot <- function(values) {
#  values = as.numeric( as.character(values ))

  ci <- boot.ci(
    boot(data=values, statistic=mean.fun, R=1000, sim="ordinary")
  )
  
  dfci = data.frame(
    ymin = round( ci$bca[,4], 2),
    ymax = round( ci$bca[,5], 2),
    y = round( mean( values ), 2)
    )
  
# S-task12  | node link
# M=3.46~[3.02,4.75]
# S-task12  | adj matrix
# M=3.43~[3.05,3.94]

  print(length(values))
  print (dfci)
  return(dfci)
}

plotData <-df %>% 
  filter( measure == "accuracy" | measure == "minutesOnTask"  )  %>% 
             # | measure == "difficulty" | measure == "confidence") %>% 
    filter( taskId == task ) %>% 
   mutate( value = as.numeric( as.character(value)) ) %>% 
   mutate( label = labels.measure[as.character(measure)] ) %>% 
     mutate( visLabel = labels.visType[as.character(visType)] ) %>% 

  mutate( label = factor(label, levels=c("Accuracy","Time (minutes)", "Confidence","Difficulty")));



# df %>% 
#   filter( measure == "accuracy" | measure == "minutesToComplete" | 
#             measure == "difficulty" | measure == "confidence") %>% 
#     filter( taskId == task ) %>% 
#   mutate( value = as.numeric( as.character(value)) ) %>% 
#   ggplot(aes(x=visType, y=value, fill=visType, color=visType)) +
#     facet_wrap(. ~ measure, scales="free", nrow=1) +
#     geom_violin() +
#     stat_summary(fun.data = "mean_cl_boot", colour = "green", size = 0.5, alpha=0.5) +
#   coord_flip() + 
#     labs(
#       title = tt,
#       subtitle = task
#     )
# 

#d=data.frame(drink=c("coffee","tea","water"), mean=c(3,6,2), lower=c(2.6,5.6,1.8), upper=c(3.5,6.3,2.8))
# ggplot() + 
# geom_pointrange(data=d, mapping=aes(x=drink, y=mean, ymin=upper, ymax=lower)) 
#
#print(d);

print(nrow(plotData))

  ggplot(data=plotData, aes(x=visLabel, y=value, fill=visType, color=visType)) +
    facet_wrap(. ~ label, scales="free", nrow=1) +
    geom_violin(show.legend=FALSE) +
  # fun.data = "mean_cl_boot"
    stat_summary(fun.data=ciboot, colour = "black", size = 0.5, alpha=.5, show.legend=FALSE) +
  coord_flip() + 
    labs(
      # title = paste(number, '-', tt),
      # subtitle = paste(number, '-', tt) , #prompt,
       # caption = paste('W=',acc_stats$W,' p=',acc_stats$'p.value', acc_stats$d, '    ', 'W=',time_stats$W,'p=',time_stats$'p.value', time_stats$d, '\n' ,ci_acc_NL$M,  ci_acc_AM$M, ci_time_NL$M, ci_time_AM$M )
      #      caption = paste(' W=',acc_stats$W,' p=',acc_stats$'p.value', acc_stats$d, '    ', '         W=',time_stats$W,'p=',time_stats$'p.value', time_stats$d, '\n' ,'NL:', ci_acc_NL$M,  'AM:', ci_acc_AM$M, '         NL:', ci_time_NL$M,'AM:', ci_time_AM$M )

    )+
    theme ( plot.margin=grid::unit(c(0,0,0,0), "mm"), plot.caption = element_text(hjust = 0, vjust =10,  face = "italic")) + 
    xlab ("") + 
    ylab("")+
    scale_fill_manual(values=visType.colors)+
    scale_color_manual(values=visType.colors)      
    # scale_y_continuous(breaks = gridLines, limits = axisRange) #,labels = gridLabels) 



# filename <- paste("violins/",gsub(" ", "", paste(number,tt), fixed = TRUE),".pdf", sep="")
#  ggsave(filename, width = 7, height = 1.5, units = "in")
}

 ggplot(data=plotData, aes(x=visLabel, y=value, fill=visType, color=visType)) +
    facet_wrap(. ~ label, scales="free", nrow=1) +
    geom_violin(show.legend=FALSE,  fill=userDriven, color=userDriven) +
  # fun.data = "mean_cl_boot"
    stat_summary(fun.data=ciboot, colour = "black", size = 0.5, alpha=.5, show.legend=FALSE) +
  coord_flip() + 
    labs(
      # title = paste(number, '-', tt),
      # subtitle = paste(number, '-', tt) , #prompt,
       # caption = paste('W=',acc_stats$W,' p=',acc_stats$'p.value', acc_stats$d, '    ', 'W=',time_stats$W,'p=',time_stats$'p.value', time_stats$d, '\n' ,ci_acc_NL$M,  ci_acc_AM$M, ci_time_NL$M, ci_time_AM$M )
      #      caption = paste(' W=',acc_stats$W,' p=',acc_stats$'p.value', acc_stats$d, '    ', '         W=',time_stats$W,'p=',time_stats$'p.value', time_stats$d, '\n' ,'NL:', ci_acc_NL$M,  'AM:', ci_acc_AM$M, '         NL:', ci_time_NL$M,'AM:', ci_time_AM$M )

    )+
    theme ( plot.margin=grid::unit(c(0,0,0,0), "mm"), plot.caption = element_text(hjust = 0, vjust =10,  face = "italic")) + 
    xlab ("") + 
    ylab("")+
    scale_fill_manual(values=visType.colors)+
    scale_color_manual(values=visType.colors)      

 # vplot('S-task03')
# 
# for (task in seq(12,12,1)){
#  vplot(paste("S-task", sprintf("%.2d",task),sep=""))
# }
```

```{r}
wtest <- function(type) {
t_manual = df_medium_hard %>% 
  filter(taskType == type & userDriven == "manual")

t_supported = df_medium_hard %>% 
  filter(taskType == type & userDriven == "supported")



# p = 0.06-- promising at the pilot level
print(type)
wilcox.test(t_manual$value, t_supported$value)
}

wtest("cluster")
wtest("linear regression")
wtest("outlier")
wtest("quadratic regression")
wtest("skyline")



```
```{r warning=FALSE}

# Bootstrap 95% CI for mean
# function to obtain mean from the data (with indexing)
mean.fun <- function(D, d) {
  return( mean(D[d]) )
}
reportCI <- function(data, attr) {
  # bootstrapping with 1000 replications
  ci <- boot.ci(
    boot(data=data[[attr]], statistic=mean.fun, R=1000, sim="ordinary")
  )

  cat( "M=",     round( mean( data[[attr]] ), 2), "~",
       "[", round( ci$bca[,4]          , 2), ",",
       round( ci$bca[,5]          , 2), "]",
       sep="")
}

citext <- function(type, measure_) {
  
df_tmp <- df %>% 
  filter(measure==measure_) 

df_tmp$value = as.numeric( as.character(df_tmp$value ))

manual = df_tmp %>% 
  filter(taskType == type & userDriven == "manual")

supported  = df_tmp %>% 
  filter(taskType == type & userDriven == "supported")

cat( paste(type," | manual\n") )
reportCI(manual, "value")
cat( "\n" )


cat( paste(type," | supported\n") )
reportCI(supported, "value")
cat( "\n" )
cat( "\n" )


}



citext('cluster', "accuracy")
citext('linear regression', "accuracy")
citext('outlier', "accuracy")
citext('quadratic regression', "accuracy")
citext('skyline', "accuracy")



```

```{r}


reportES <- function(data, attr, group) {

  lvs <- levels(data[[group]])

  b <- bootES(data,
              data.col=attr,
              group.col=group,
              contrast=lvs, # normal cases c(group1=1, group2=-1), but for 2 groups, it's simplified.
              effect.type="cohens.d")

  cat( "d=", round( b$t0, 2), "~",
       "[", round( b$bounds[1], 2), ",",
       round( b$bounds[2], 2), "]",
       sep="")
}

estext <- function(type, measure_) {
  
df_tmp <- df %>% 
  filter(measure==measure_) 

df_tmp$value = as.numeric( as.character(df_tmp$value ))

esd = df_tmp %>% 
  filter(taskType == type)

cat( paste(type, "\n") )
reportES(esd, "value", "userDriven")
cat( "\n" )
cat( "\n" )


}


estext("cluster", "accuracy")
estext("linear regression", "accuracy")
estext("outlier", "accuracy")
estext("quadratic regression", "accuracy")
estext("skyline", "accuracy")
```





```{r fig.width=5, fig.height=4 }
 df_acc %>% 
  ggplot( aes(x=userDriven, y=value) ) +
    geom_jitter( shape=1 , color='grey', position = position_jitter(w = 0.3, h = 0)) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.5) +
  # ylim(0,100) +
   # xlim(-.25,.25) +
  coord_flip() +
    facet_grid(taskDifficulty ~ .)+
    theme(strip.text.y = element_text(angle=0))

#   
# 
# # testData <- ggplot_build(g)$data
# std <- ggplot_build(g)$data[[2]]
# print (std)
# 
# # //add userDriven column
# 
# std$userDriven <- ifelse(std$PANEL==1, "manual", "supported")
# g + geom_text(data = std,
#               aes(x = x, y = 0.1, label = round(y,3)),
#               color = "blue", size=3,
#               vjust = 1)  +
#   facet_grid(. ~ userDriven)+
#    labs(y="Accuracy", x = 'Task Difficulty')


```


```{r fig.width=5, fig.height=8}
g<- df_acc %>% 
  ggplot( aes(x=0, y=value) ) +
    geom_jitter( shape=1 , color='grey', position = position_jitter(w = 0.3, h = 0)) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.5) +
  # ylim(0,100) +
   xlim(-.25,.25) +
  coord_flip() +
    facet_grid(. ~ userDriven)

# testData <- ggplot_build(g)$data
sat <- ggplot_build(g)$data[[2]]
print (sat)

# //add userDriven column

sat$userDriven <- ifelse(sat$PANEL==1, "manual", "supported")
g + geom_text(data = sat,
              aes(x = x, y = 0.1, label = round(y,3)),
              color = "blue", size=3,
              vjust = 1)  +
  facet_grid(. ~ userDriven)+
   labs(y="Accuracy", x = '')


 
```

we can do the same with distributions, ridges

```{r}
df %>% 
  filter(measure=="accuracy") %>% 
  mutate( value = as.numeric(as.character(value)) ) %>% 
  ggplot( aes(x=value, y=taskId) ) +
    geom_density_ridges() +
    facet_grid(. ~ userDriven)

```


, and density plots (look meh-- could probably combine + color for a better look)

```{r, fig.height=10, fig.width=10}

df %>% 
  filter(measure=="accuracy") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot( aes(value) ) +
    geom_density( alpha = 0.2 ) +
    facet_grid(taskId ~ userDriven)

```


## Power Analysis

```{r}

powerAnalysisGraph <- function(m1, m2, stdev, iterNum=15){
  # stdev <- sd_duration.median
  # m1 <- mean(search$duration.median)
  # m2 <- mean(nonsearch$duration.median)
  # # m1 <- mean(foresight$duration.median)
  # # m2 <- mean(nonsearch$duration.median)
  
  iteration <- 15
  
  difference <- 0
  effectSize <- 0
  numParticipants <- 0
  
  for(step in 1:iteration)
  {
    difference[step] <- abs(m1 - m2) * (0.9 ^ (step-1))
    effectSize[step] <- difference[step] / stdev
    numParticipants[step] <- pwr.t.test( 
      d=effectSize[step], 
      sig.level=.05, 
      power=0.8, 
      # type="two.sample", 
      type="paired",
      alternative="greater" 
    )$n * 1.15 * 2
  }
  
  #dual axis code online: https://rpubs.com/kohske/dual_axis_in_ggplot2
  grid.newpage()
  
  pw <- data.frame(difference=difference, numParticipants=numParticipants, effectSize=effectSize)
  p1 <- ggplot(pw,aes(x=difference)) + geom_line(aes(y = numParticipants)) +
    scale_y_continuous(breaks = pretty(pw$numParticipants, n = 10))
  p2<- ggplot(pw,aes(x=difference)) + geom_line(aes(y = effectSize)) +
    theme(panel.background = element_rect(fill = NA))+
    scale_y_continuous(breaks = pretty(pw$effectSize, n = 10))
  p2
  
  # extract gtable
  g1 <- ggplot_gtable(ggplot_build(p1))
  g2 <- ggplot_gtable(ggplot_build(p2))
  
  # overlap the panel of 2nd plot on that of 1st plot
  pp <- c(subset(g1$layout, name == "panel", se = t:r))
  g <- gtable_add_grob(g1, g2$grobs[[which(g2$layout$name == "panel")]], pp$t, pp$l, pp$b, pp$l)
  
  # axis tweaks
  ia <- which(g2$layout$name == "axis-l")
  ga <- g2$grobs[[ia]]
  ax <- ga$children[[2]]
  ax$widths <- rev(ax$widths)
  ax$grobs <- rev(ax$grobs)
  ax$grobs[[1]]$x <- ax$grobs[[1]]$x - unit(1, "npc") + unit(0.15, "cm")
  g <- gtable_add_cols(g, g2$widths[g2$layout[ia, ]$l], length(g$widths) - 1)
  g <- gtable_add_grob(g, ax, pp$t, length(g$widths) - 1, pp$b)
  

  # draw it
  grid.draw(g)
  
  return (g)
  
}

```


then, we test it out with some parameters estimated by eye from our charts so far

```{r}
# allTasks (reading values from graph, could do exact later)
# powerAnalysisGraph(0.8329050	, 0.8625925, 0.25)


# Find all unique taskTypes
taskGroups <- (df_acc$taskType)

for (group in unique(taskGroups)){
  
  gr<-group
   print (gr)
  
  
  data <- df_acc %>% 
  filter(taskType == gr) %>% 
  filter(taskDifficulty != 'easy')
  
  
  # print (data)

  sd_bothConditions =
    data %>%
  summarise(
    stdev = sd(value)
  )

mean_manual = data %>%
  filter(userDriven == "manual") %>% 
  summarise(
    mean = mean(value)
  )

mean_supported = data %>%
  filter(userDriven == "supported") %>% 
  summarise(
    mean = mean(value)
  )

# print(mean_manual,mean_supported,sd_bothConditions)
powerAnalysisGraph(mean_manual[,1],mean_supported[,1],sd_bothConditions[,1])

  
}
```


```{r}
# Find all  unique task Difficulties;
taskDifficulties <- df_acc$taskDifficulty

for (difficulty in unique(taskDifficulties)){

  print (difficulty)
  data <- df_acc %>% 
  filter(taskDifficulty == difficulty) 
  
  
  # print (data)

  sd_bothConditions =
    data %>%
  summarise(
    stdev = sd(value)
  )

mean_manual = data %>%
  filter(userDriven == "manual") %>% 
  summarise(
    mean = mean(value)
  )

mean_supported = data %>%
  filter(userDriven == "supported") %>% 
  summarise(
    mean = mean(value)
  )

print(mean_manual,mean_supported,sd_bothConditions)
powerAnalysisGraph(mean_manual[,1],mean_supported[,1],sd_bothConditions[,1])

  
}

```




```{r}


# allTasks
sd_allTasks = df_acc %>% 
  # filter(taskId == "S-task08") %>% 
  summarise(
    stdev = sd(value)
  )

mean_manual = df_acc %>% 
  filter(userDriven == "manual") %>% 
  summarise(
    mean = mean(value)
  )

mean_supported = df_acc %>% 
  filter(userDriven == "supported") %>% 
  summarise(
    mean = mean(value)
  )

g<-powerAnalysisGraph(mean_manual[,1],mean_supported[,1],sd_allTasks[,1])

# print (g)

# title <- textGrob("Title",gp=gpar(fontsize=50))
#  gtable_add_grob(
#     g, 
#     title, 
#     1, 1, 1, ncol(g))

# gtable_add_rows(g, heights = grobHeight(title) + padding,
# +                          pos = 0)
```

Now we want to get better estimates for parameters.
We need Means from each group, on each task, and a pooled stdev.

```{r}

# task 08
sd_t08 = df_acc %>% 
  filter(taskId == "S-task08") %>% 
  summarise(
    stdev = sd(value)
  )

m_nl_t08 = df_acc %>% 
  filter(taskId == "S-task08" & visType == "nodeLink") %>% 
  summarise(
    mean = mean(value)
  )

m_adj_t08 = df_acc %>% 
  filter(taskId == "S-task08" & visType == "adjMatrix") %>% 
  summarise(
    mean = mean(value)
  )

# task 13
sd_t13 = df_acc %>% 
  filter(taskId == "S-task13") %>% 
  summarise(
    stdev = sd(value)
  )

m_nl_t13 = df_acc %>% 
  filter(taskId == "S-task13" & visType == "nodeLink") %>% 
  summarise(
    mean = mean(value)
  )

m_adj_t13 = df_acc %>% 
  filter(taskId == "S-task13" & visType == "adjMatrix") %>% 
  summarise(
    mean = mean(value)
  )

```
... and now some more accurate power analysis graphs

```{r}

powerAnalysisGraph(m_adj_t08[,1], m_nl_t08[,1], sd_t08[,1])

powerAnalysisGraph(m_adj_t13[,1], m_nl_t13[,1], sd_t13[,1])

```



Interpreting the task 13 graph: 
"Given no changes in Means or pooled stdev, and assuming a t-test, you'd need ~225 people total to find a medium effect size."


## Rank-style tests

Given the data isn't technically continuous at the measurement level, we might consider non-parametric tests:

```{r}
t13_nl = df_acc %>% 
  filter(taskId == "S-task13" & visType == "nodeLink")

t13_adj = df_acc %>% 
  filter(taskId == "S-task13" & visType == "adjMatrix")

# p = 0.06-- promising at the pilot level
wilcox.test(t13_nl$value, t13_adj$value)
```

```{r}
wtest <- function(task) {
t_manual = df_acc %>% 
  filter(taskId == task & userDriven == "manual")

t_supported = df_acc %>% 
  filter(taskId == task & userDriven == "supported")

# p = 0.06-- promising at the pilot level
print(task)
wilcox.test(t_manual$value, t_supported$value)
}

wtest("0")
      
wtest("0")
```


## CIs

```{r, warning=FALSE}

# Bootstrap 95% CI for mean
# function to obtain mean from the data (with indexing)
mean.fun <- function(D, d) {
  return( mean(D[d]) )
}

reportCI <- function(data, attr) {
  # bootstrapping with 1000 replications
  ci <- boot.ci(
    boot(data=data[[attr]], statistic=mean.fun, R=1000, sim="ordinary")
  )

  cat( "M=",     round( mean( data[[attr]] ), 2), "~",
       "[", round( ci$bca[,4]          , 2), ",",
       round( ci$bca[,5]          , 2), "]",
       sep="")
}

citext <- function(task, measure_) {
  
df_tmp <- df %>% 
  filter(measure==measure_) 

df_tmp$value = as.numeric( as.character(df_tmp$value ))

nl = df_tmp %>% 
  filter(taskId == task & visType == "nodeLink")

adj = df_tmp %>% 
  filter(taskId == task & visType == "adjMatrix")

cat( paste(task," | node link\n") )
reportCI(nl, "value")
cat( "\n" )


cat( paste(task," | adj matrix\n") )
reportCI(adj, "value")
cat( "\n" )
cat( "\n" )


}
# cat("\n\n =========ACCURACIES======== \n\n")
# 
# citext("S-task01", "accuracy")
# citext("S-task02", "accuracy")
# citext("S-task03", "accuracy")
# citext("S-task04", "accuracy")
# citext("S-task05", "accuracy")
# citext("S-task06", "accuracy")
# citext("S-task07", "accuracy")
# citext("S-task08", "accuracy")
# citext("S-task09", "accuracy")
# citext("S-task10", "accuracy")
# citext("S-task11", "accuracy")
# citext("S-task12", "accuracy")
# citext("S-task12A", "accuracy")
# citext("S-task12B", "accuracy")
# citext("S-task13", "accuracy")
# citext("S-task14", "accuracy")
# citext("S-task15", "accuracy")
# #citext("S-task16", "accuracy")
# 
 cat("\n\n =========TIMES======== \n\n")
# 
# citext("S-task01", "minutesOnTask")
# citext("S-task02", "minutesOnTask")
# citext("S-task03", "minutesOnTask")
# citext("S-task04", "minutesOnTask")
# citext("S-task05", "minutesOnTask")
# citext("S-task06", "minutesOnTask")
# citext("S-task07", "minutesOnTask")
# citext("S-task08", "minutesOnTask")
# citext("S-task09", "minutesOnTask")
# citext("S-task10", "minutesOnTask")
# citext("S-task11", "minutesOnTask")
# citext("S-task12", "minutesOnTask")
# citext("S-task13", "minutesOnTask")
# citext("S-task14", "minutesOnTask")
# citext("S-task15", "minutesOnTask")
# citext("S-task16", "minutesOnTask")


for (task in seq(1,16,1)){
  citext(paste("S-task", sprintf("%.2d",task),sep=""),"minutesOnTask")

}

# cat("\n\n =========DIFFICULTY======== \n\n")
# for (task in seq(1,16,1)){
#   citext(paste("S-task", sprintf("%.2d",task),sep=""),"difficulty")
# 
# }
# 
# cat("\n\n =========CONFIDENCE======== \n\n")
# for (task in seq(1,16,1)){
#     citext(paste("S-task", sprintf("%.2d",task),sep=""),"confidence")
# 
# }


```


## Effect Sizes

Note: at least as of 10-Sep-2019, negative effect sizes appear to mean "the adjMatrix wins" aka the adjMatrix has a higher accuracy

```{r, warning=FALSE}


reportES <- function(data, attr, group) {

  lvs <- levels(data[[group]])

  b <- bootES(data,
              data.col=attr,
              group.col=group,
              contrast=lvs, # normal cases c(group1=1, group2=-1), but for 2 groups, it's simplified.
              effect.type="cohens.d")

  cat( "d=", round( b$t0, 2), "~",
       "[", round( b$bounds[1], 2), ",",
       round( b$bounds[2], 2), "]",
       sep="")
}

estext <- function(task, measure_) {
  
df_tmp <- df %>% 
  filter(measure==measure_) 

df_tmp$value = as.numeric( as.character(df_tmp$value ))

esd = df_tmp %>% 
  filter(taskId == task)

cat( paste(task, "\n") )
reportES(esd, "value", "visType")
cat( "\n" )
cat( "\n" )


}
cat("\n\n =========ACCURACIES======== \n\n")

estext("S-task01", "accuracy")
estext("S-task02", "accuracy")
estext("S-task03", "accuracy")
estext("S-task04", "accuracy")
estext("S-task05", "accuracy")
estext("S-task06", "accuracy")
estext("S-task07", "accuracy")
estext("S-task08", "accuracy")
estext("S-task09", "accuracy")
estext("S-task10", "accuracy")
estext("S-task11", "accuracy")
estext("S-task12", "accuracy")
estext("S-task13", "accuracy")
estext("S-task14", "accuracy")
estext("S-task15", "accuracy")
#estext("S-task16", "accuracy")

cat("\n\n =========TIMES======== \n\n")

estext("S-task01", "minutesOnTask")
estext("S-task02", "minutesOnTask")
estext("S-task03", "minutesOnTask")
estext("S-task04", "minutesOnTask")
estext("S-task05", "minutesOnTask")
estext("S-task06", "minutesOnTask")
estext("S-task07", "minutesOnTask")
estext("S-task08", "minutesOnTask")
estext("S-task09", "minutesOnTask")
estext("S-task10", "minutesOnTask")
estext("S-task11", "minutesOnTask")
estext("S-task12", "minutesOnTask")
estext("S-task13", "minutesOnTask")
estext("S-task14", "minutesOnTask")
estext("S-task15", "minutesOnTask")
estext("S-task16", "minutesOnTask")
```

## TODO Subtract CIs?

## TODO Tidybayes-style eye plots (in progress + may be abandoned)

```{r}
# df %>% 
#   filter(measure=="accuracy") %>% 
#   mutate( value = as.numeric(value) ) %>% 
#   ggplot( aes(x=taskId, dist="norm", arg1=value) ) +
#   geom_halfeyeh() +
  


m_acc = lm(value ~ taskId, data = df_acc)

summary(m_acc)

tidy(m_acc)

m_acc %>%
  tidy() %>%
  ggplot() +
  geom_halfeyeh( aes(x=term, y=estimate)) 


```


## Participant Info

```{r}
fct_unique(dfp$measure)

dfp %>% 
  filter(measure == "age") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot() +
    geom_density( aes(x=value), fill="blue", alpha=0.75 ) 

dfp %>% 
  filter(measure == "age") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot(aes(x="age", y=value)) +
    geom_beeswarm(priority='random',cex=2, alpha=0.6) +
  coord_flip() +
  xlab("") + ylab("")

```


## Task Beeswarms

```{r, fig.width=8, fig.height=2}

fct_unique(df$measure)

# TODO scales fix for each measure (make global plot and use to fix scales)... but have to do for each measure!
# TODO color choices could be better
# TODO figure width and height?
# TODO manual order for measures?

vplot <- function(task) {

sdf = df %>% filter( taskId == task )
tt = as.character(sdf[1,]$taskTitle)

df %>% 
  filter( measure == "accuracy" | measure == "minutesToComplete" | 
            measure == "difficulty" | measure == "confidence") %>% 
    filter( taskId == task ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot(aes(x=visType, y=value, fill=visType, color=visType)) +
    facet_wrap(. ~ measure, scales="free", nrow=1) +
    geom_violin() +
    stat_summary(fun.data = "mean_cl_boot", colour = "green", size = 0.5, alpha=0.5) +
  coord_flip() + 
    labs(
      title = tt,
      subtitle = task
    )
  
ggsave(paste("violins/",task,".pdf", sep=""), width = 10, height = 2.5, units = "in")
}

vplot("S-task01")
vplot("S-task02")
vplot("S-task03")
vplot("S-task04")
vplot("S-task05")
vplot("S-task06")
vplot("S-task07")
vplot("S-task08")
vplot("S-task09")
vplot("S-task10")
vplot("S-task11")
vplot("S-task12")
vplot("S-task13")
vplot("S-task14")
vplot("S-task15")
vplot("S-task16")

```


## Beeswarm debugging


## Grouped Charts

T1/T2

T4/T5

T10/T11

T13/T14

```{r, fig.width=10, fig.height=6}

df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task01" | taskId == "S-task02" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task01_S-task02.pdf")

df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task04" | taskId == "S-task05" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task04_S-task05.pdf")


df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task10" | taskId == "S-task11" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task10_S-task11.pdf")

df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task13" | taskId == "S-task14" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task13_S-task14.pdf")



```

## S-Task12 debugging

```{r}
df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task12") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot(aes(x=visType, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.01  ) + 
  coord_flip()
```

